---
title: "iteration_and_listcols"
author: "Farizah Rob"
date: "2022-11-01"
output: html_document
---

```{r}
library(tidyverse)

set.seed(1)
```

##Lists

Lists provide a way to store anything you want. This flexibility is great, but is offset by a certain … clunkiness. Lists contain indexed elements, and the indexed elements themselves be scalars, vectors, or other things entirely.

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

```{r}
l <- list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```

```{r}
l$vec_numeric

l[[1]] #first element of the list

l[[1]][1:3] #first element of the list -> first three elements of that element
```

```{r}
list_norms <- 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```

```{r}
mean_and_sd <- function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}

mean_and_sd(list_norms[[1]])

output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}

output
```
## can we map? 

`map` function 

```{r}
output <- map(list_norms, mean_and_sd)

output <- map(.x = list_norms, ~ mean_and_sd(.x))
```

so...what about other functions? 

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = median(list_norms[[i]])
}

output <- map(list_norms, median)
```

`map` variants...

```{r}
#double
output <- map_dbl(list_norms, median, .id = "input")
output

#output as a data frame
output <- map_dfr(list_norms, mean_and_sd, .id = "input")
output
```

## list columns 

```{r}
listcol_df <- 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )

listcol_df

listcol_df %>% pull(name)

listcol_df %>% pull(samp)

output <- map(listcol_df$samp, mean_and_sd)
```

can we add list columns, and then what

```{r}
listcol_df <- 
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd)) %>%
  select(-samp)
```

Nested data

```{r}
weather_df <-
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_nest <- 
  nest(weather_df, data = date:tmin)

weather_nest
```

```{r}
weather_nest %>% pull(name)

weather_nest %>% pull(data)
```

Creating a linear regression function and mapping it to the weather data frame
```{r}
weather_lm <- function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest$data[[1]])

map(weather_nest$data, weather_lm)

map(weather_nest[["data"]], weather_lm)

#without explicitly defining a function from before

map(weather_nest$data, ~lm(tmax ~ tmin, data = .x))
```

Using `mutate` to fit this model and store it in the data frame

Can I do all this in a tidy way?

```{r}
weather_nest <- 
  weather_nest %>% 
  mutate(models = map(data, weather_lm))

weather_nest
```


unnesting

```{r}
weather_nest %>%
  unnest(data)
```

## Revisiting Napolean Dynamite

```{r}
library(rvest)
```

```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```


What we did last time

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

Using a `for loop` and `bind rows`
Or using `map df`

```{r}
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews <- bind_rows(output)

dynamite_reviews <- map_df(vec_urls, read_page_reviews)

dynamite_reviews <- 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest()

dynamite_reviews <- dynamite_reviews %>% 
  select(-page)
```

